### 2017-03-29 thesis/latex/thesis.tex

@@

\section{Chapter: Introduction}

Begin with a paper-like introduction which talks about:

>>>>

\usepackage{epigraph}

@@

\section{Chapter: Introduction}
\subsection{Grabber}

\epigraph{An embryo in its spherical blastula stage has spherical symmetry [...]. But a system which has spherical symmetry, and whose state is changing because of chemical reactions and diffusion, will remain spherically symmetrical for ever [...]. It certainly cannot result in an organism such as a horse, which is not spherically symmetrical.}{Alan Turing, The Chemical Basis of Morphogenesis, 1952}

A fundamental faculty cells require to control their internal environments is the ability to create and maintain asymmetry. Diffusion, as per above, is an undirected process which cannot create asymmetry. How, then, do cells meet this need?\\

Motor proteins are structures which use energy to create directed motion in cells. In broad terms, they are creators of asymmetry. This thesis will explore a hypothesis on how one such motor protein, Dynein, achieves this.\\

\subsection{Interest builder}
Begin with a paper-like introduction which talks about:
